### 2019-11-15 report/05-stability.Rmd
Add fine analysis of the CV

```{r less-stab-troph, fig.dim = c(10, 7), fig.cap = "The four station with the lowest biomass stability. See caption of Figure for details."}
plot_grid(plotlist = plot_stab[7:8], ncol = 2)
```

@@

```{r 25-stab-troph, fig.dim = c(10, 7), fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
# Third quater
plot_stab <- purrr::map(sync_sp_troph$station[104:107], function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab[1:10], ncol = 2)
```

@@

```{r abun-sp, fig.cap = "Species most abundant by trophic group."}
# Sp the most abundant by group
bm_sp_troph_grp <- net_sp_troph %>%
  filter(!is.na(troph_group) & troph_group != 1) %>%
  group_by(troph_group, sp_class) %>%
  summarise(biomass = mean(biomass)) %>%
  arrange(desc(biomass)) %>%
  slice(1:20)

@@

@@

```{r}
cv_sp_grp <- left_join(select(cv_bm_sp, -bm),
  select(cv_bm_div_troph_grp, -biomass_stab), by = "station")

ang9 <- cv_sp_grp %>%
  filter(species == "ANG_9")

@@

@@

```{r, fig.dim = c(10, 7)}
ggplot(high_div_troph_group_3,
  aes(y = biomass, x = date, color = troph_group)) +
  geom_line() +
  geom_point() +
  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
    x = ymd_hms("2015-01-01T15:00:00"),
    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
    size = 6, inherit.aes = FALSE) +
  facet_wrap( ~ station) + 
  labs(title = "The twelve richest station of superior predator",
  y = "Fish species richness", x = "Date")
```

@@

```{r}
myload(station_analysis, region_polygon, dir = data_common)
stab <- temporal_community_metrics %>% 
  select(station, biomass_stab)
station_stab <- left_join(station_analysis, rename(stab, id = station)) %>%
  filter(!is.na(biomass_stab))
ggplot(data = region_polygon) +
    geom_sf() +
    geom_sf(data = station_stab, aes(color = log(biomass_stab)), size = 4) +
    scale_color_gradient(low = "red", high = "green")
```

>>>>

```{r less-stab-troph, fig.dim = c(10, 7), fig.cap = "The four station with the lowest biomass stability. See caption of Figure for details."}
plot_grid(plotlist = plot_stab[7:10], ncol = 2)
```

@@

```{r 25-stab-troph, fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
# Third quater
plot_stab <- purrr::map(sync_sp_troph$station[104:107], function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab[1:10], ncol = 2)
```

@@

```{r abun-sp, fig.dim = c(10, 7), fig.cap = "Species most abundant by trophic group."}
# Sp the most abundant by group
bm_sp_troph_grp <- net_sp_troph %>%
  filter(!is.na(troph_group) & troph_group != 1) %>%
  group_by(troph_group, sp_class, opcod) %>%
  mutate(rel_biomass = biomass / sum(biomass)) %>%
  group_by(troph_group, sp_class) %>%
  summarise(sum_rel_bm = sum(rel_biomass), biomass = mean(biomass)) %>%
  arrange(desc(sum_rel_bm)) %>%
  slice(1:20)

@@

#### Diversity is not all

```{r}
library(ade4)
library(factoextra)
myload(habitat_pressure, dir = mypath("report"))
```

```{r}
div_troph_grp <- cv_bm_div_troph_grp %>%
  select(station, troph_group, cv_st) %>%
  spread(key = troph_group, cv_st) %>%
  rename(mid_cv = `2`, high_cv = `3`)

hab_press_div <- left_join(habitat_pressure,
  temporal_community_metrics[, c("station", "richness_med", "biomass_avg","biomass_stab")],
  by = "station") %>%
left_join(div_troph_grp, by = "station")
pca_hab <- dudi.pca(as.data.frame(select(na.omit(hab_press_div), -station)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE)

eig_plot <- fviz_eig(pca_hab)
pca_plot <- fviz_pca_var(pca_hab,
    axes = c(1, 2),
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )

ggdraw(pca_plot) + 
  draw_plot(eig_plot, x = .9, y = .95, hjust = 1, vjust = 1, width = 0.17, height = 0.25)
```

```{r}
m <- cor(as.matrix(select(na.omit(hab_press_div), -station)), method =
  "spearman")
corrplot::corrplot(m, order="hclust")
```

```{r, eval = FALSE}
mod <- lm(high_cv ~ temperature + richness_med:temperature + DBO + lat + insecticides + herbicides + insecticides, hab_press_div)
car::vif(mod)

mod <- lm(mid_cv ~ richness_med + DBO + lat + temperature + insecticides + herbicides + insecticides, hab_press_div)
car::vif(mod)
```

#### Assembly rules: richness and biomass distribution

One missing part was the fact that we do not know the assembly rules of the
trophic group.

```{r}
cv_bm_div_troph_grp %>%
  ggplot(aes(y = cv_st, x = div_st)) +
  geom_point() +
  facet_grid(cols = vars(troph_group))
```

```{r}
sync_com_troph <- net_sp_troph %>%
    rename(species = sp_class) %>%
    filter(troph_group != 1) %>%
    mutate(troph_group = as.factor(troph_group)) %>%
    group_by(troph_group) %>%
    nest() %>%
    mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>%
    unnest(sync) %>%
    mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
    select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev) %>%
    left_join(cv_bm_div_troph_grp, by = c("station", "troph_group"))
```

```{r sd-avg-div}
form <- y ~ x
form2 <- y ~ Vmax * x / (Km + x)
form3 <- y ~  a + exp(b * x) 
fit <- stat_poly_eq(
  formula = form2,
  eq.with.lhs = "italic(hat(y))~`=`~",
  aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
  parse = TRUE)

ymax <- max(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
ymin <- min(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
p_bm <- cv_bm_div_troph_grp %>%
  ggplot(aes(y = bm_st, x = div_st)) +
  geom_point() +
  geom_smooth(method = 'nls', formula = form3,
   method.args = list(start = c(a = 0, b = 3)), se = F) +
  #fit +
  facet_grid(cols = vars(troph_group)) +
  #scale_y_log10(limits = c(ymin, ymax)) +
  labs(y = "Average biomass (g).", x = "Species richness")

p_sd <- sync_com_troph %>%
  ggplot(aes(x = div_st, y = sdt.dev)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  fit +
  facet_grid(cols = vars(troph_group)) +
  scale_y_log10(limits = c(ymin, ymax)) +
  labs(y = "Standard deviation of biomass temporal data (g).", x = "Species richness")

plot_grid(p_sd, p_bm, ncol = 1)
```
It seems that the relationship between the standard deviation and the number of
species saturates for 10 species in medium trophic group while it saturates at 7
for the high trophic group (Figure \@ref(fig:sd-avg-div)).

To get opposite stability-diversity relationships in the different trophic
group, it supposes that for medium trophic group, the avg biomass increases
faster than the biomass standard deviation with increasing species richness. And
the reverse for the high trophic group, i.e. that the standard deviation
increases faster than the average biomass.

A question: What are the determinant of the relationship beween avg/standard
deviation and the number of species?

Part of the solution

```{r}
formula <- y ~ x #needed for stat_poly_eq
sync_com_troph %>%
  ggplot(aes(x = bm_st, y = sdt.dev)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  facet_grid(cols = vars(troph_group)) +
  scale_y_log10() +
  scale_x_log10() +
  labs(y = "Standard deviation of biomass temporal data (g).", x = "Average
      biomass (g)")
```

```{r}

@@

There was a positive relationship between the species CV of the most abundant
species in the high trophic group and the CV of the same high trophic group
(Figure \@ref(fig:cv-sp-grp3), right panel). Interestingly, this relationship
is less clear (however clearly present for some species) for the most abundant
species in the medium trophic group (Figure \@ref(fig:cv-sp-grp2), right panel).

```{r cv-sp-grp3, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the CV of the different trophic groups"}
cv_sp_grp <- left_join(select(cv_bm_sp, -bm),
  select(cv_bm_div_troph_grp, -biomass_stab), by = "station")

sp_grp3 <- bm_sp_troph_grp %>%
  filter(troph_group == 3) %>%
  arrange(desc(biomass))

cv_sp_grp %>%
  filter(species %in% sp_grp3$sp_class[1:10]) %>%
  ggplot(aes(x = cv_st, y = cv)) +
  geom_point() +
  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller())) +
  labs(x = "CV of the trophic group", y = "CV of the species")
```

```{r cv-sp-grp2, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the medium trophic group versus the CV of the different trophic groups"}
sp_grp2 <- bm_sp_troph_grp %>%
  filter(troph_group == 2) %>%
  arrange(desc(biomass))

cv_sp_grp %>%
  filter(species %in% sp_grp2$sp_class[1:10]) %>%
  ggplot(aes(x = cv_st, y = cv)) +
  geom_point() +
  facet_grid(cols = vars(troph_group), rows = vars(species), labeller =
    labeller(troph_group = troph_group_labeller())) +
  labs(x = "CV of the trophic group", y = "CV of the species")
```

#### CVsp versus Biomass by trophic group

```{r cv-sp-bm-grp3, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the biomass of the different trophic groups"}
cv_sp_grp %>%
  filter(species %in% sp_grp3$sp_class[1:10]) %>%
  ggplot(aes(x = bm_st, y = cv)) +
  geom_point() +
  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller()),
    scales = "free_x") +
  labs(x = "Biomass of the trophic group (g)", y = "CV of the species")

@@

```{r cv-sp-bm-grp2, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the medium trophic group versus the biomass of the different trophic groups"}
cv_sp_grp %>%
  filter(species %in% sp_grp2$sp_class[1:10]) %>%
  ggplot(aes(x = bm_st, y = cv)) +
  geom_point() +
  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller()),
    scales = "free_x") +
  labs(x = "Biomass of the trophic group (g)", y = "CV of the species")
```

#### CVsp versus diversity by trophic group

```{r cv-sp-div-grp3, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the species richness in the different trophic groups."}
cv_sp_grp %>%
  filter(species %in% sp_grp3$sp_class[1:10]) %>%
  ggplot(aes(x = div_st, y = cv)) +
  geom_point() +
  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller())) +
  labs(x = "Species richness of the trophic group", y = "CV of the species")
```

```{r cv-sp-div-grp2, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the medium trophic group versus the species richness in the different trophic groups."}
cv_sp_grp %>%
  filter(species %in% sp_grp2$sp_class[1:10]) %>%
  ggplot(aes(x = div_st, y = cv)) +
  geom_point() +
  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller())) +
  labs(x = "Species richness of the trophic group", y = "CV of the species")
```

#### Temporal dynamics in high diversity community

@@

```{r, fig.dim = c(10, 7)}
ggplot(high_div_troph_group_3,
  aes(y = biomass, x = date, color = troph_group)) +
  geom_line() +
  geom_point() +
  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
    x = ymd_hms("2015-01-01T15:00:00"),
    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
    size = 6, inherit.aes = FALSE) +
  facet_wrap( ~ station) + 
  labs(title = "The twelve richest station of superior predator",
  y = "Biomass of trophic group (g)", x = "Date")
```

```{r}
ggplot(high_div_troph_group_3,
  aes(y = biomass, x = date, color = troph_group)) +
  geom_line() +
  geom_point() +
  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
    x = ymd_hms("2015-01-01T15:00:00"),
    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
    size = 6, inherit.aes = FALSE) +
  facet_wrap( ~ station) + 
  labs(title = "The twelve richest station of superior predator",
  y = "Biomass of trophic group (g)", x = "Date")
```

@@

```{r map-stab, fig.cap = "Repartition of average biomass and biomass stability (logged)."}
myload(station_analysis, region_polygon, dir = data_common)
stab <- temporal_community_metrics %>% 
  select(station, biomass_stab, biomass_avg)
station_stab <- left_join(station_analysis, rename(stab, id = station)) %>%
  filter(!is.na(biomass_stab))
map_stab <- ggplot(data = region_polygon) +
    geom_sf() +
    geom_sf(data = station_stab, aes(color = log(biomass_stab)), size = 4) +
    scale_color_gradient(low = "red", high = "green") +
    labs(title = "Biomass stability")

map_bm <- ggplot(data = region_polygon) +
    geom_sf() +
    geom_sf(data = station_stab, aes(color = log(biomass_avg)), size = 4) +
    scale_color_gradient(low = "red", high = "green") +
    labs(title = "Average biomass (g)")

plot_grid(map_stab, map_bm, ncol = 2)
```

Biomass stability was lower in south-west of France (Figure
\@ref{fig:map-stab}, left panel). Average fish biomass was lower in moutain
region (Pyrénées, Alps, Massif Central; Figure \@ref{fig:map-stab}, right
panel), generally close to the source.

```{r map-st, fig.dim = c(7, 15), fig.cap = "Repartition of the average biomass, biomass stability and species diversity by trophic group, respectively medium and high for the left and right panel. All the metrics were logged."}
tmp <- rename(cv_bm_div_troph_grp, id = station)
station_troph_div <- left_join(station_analysis, tmp, by = "id")

map_st_metrics <- purrr::map(c("bm_st", "div_st", "biomass_stab"), function (metric) {
  station_troph_div[[metric]] <- log10(station_troph_div[[metric]])
  ggplot(data = region_polygon) +
    geom_sf() +
    geom_sf(data = station_troph_div, aes_(color = as.name(metric)), size = 4) +
    facet_grid(cols = vars(troph_group)) +
    scale_color_gradient(low = "red", high = "green")

  })
plot_grid(plotlist = map_st_metrics, ncol = 1)
```

The biomass in both trophic groups were lower in moutain area (Figure
\@ref(map-st)), the same was true for species diversity. For stability, it is
difficult to see a pattern.
